---
title: "extract-scales-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{extract-scales-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ENMSat)
library(raster)
```

# Package data
Inspect data from ENMSat
```{r}
data("tree_cover")
plot(tree_cover)
```

## Package function
The function `stract_scales` can extract values (from occurrence points) of remote sensing predictors at different spatial resolutions. The resolution are resampled with an aggregation factor of 5 and 3.

```{r}
#loading remote sensing raster file from the package
data("tree_cover")
# Sampling 25 random points within the raster
points_test <- sampleRandom(tree_cover, size=25, cells=FALSE, sp=TRUE)
plot(tree_cover)
plot(points_test, add = TRUE)

df <- extract_scales(tree_cover, points_test)
df
```
v1, v2, and v3 in this example are the variable extracted at ~1km (original raster resolution), ~5km and ~10km resolution, respectively.

--------------
